---
title: "Amazon Tablet Reviews Analysis"
author: "Batul Arsiwala"
date: "March 10, 2017"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                       warning=FALSE, message=FALSE)
```

```{r}

library(dplyr)
library(stringr)
library(tidyr)
library(reshape2)
library(magrittr)
library(tm)
library(koRpus)
library(textclean) 
library(ANLP)
library(slam)
library(wordcloud)
library(ggplot2)
library(repr)
```

#Analysis of the Tablet reviews obtained from Amazon

#Data Loading

```{r}
rd = read.csv("C:/Users/Murtaza/Desktop/SCU NOTES/Machine Learning/ML_Project/Project files/amazon_reviews.csv",na.strings=c("","NA"))

# Lets look at the shape of the dataset
dim(rd)

# Column names
colnames(rd)
```

As we can see the dataset consists of 40,741 reviews of all different types of Tablets available on Amazon.

#Extracting top feature of tablets from all reviews

```{r}
# Creating a lexicon for tablet features
tablet_lexicon = c()

##Attaching words associated with weight 
weight = c("weight", "heavy", "light", "portable", "portability", "lightweight", "size", "small", "carry","compact","pocketsized","pocketsize")

##Attaching words associated with Display & Media 
display_media = c("display", "screen", "widescreen", "touch", "video", "resolution", "brightness", "audio","bright","touchscreen","graphics","graphic")

##Attaching words associated with Processor
processor = c("processor", "speed", "lag", "lags", "slow", "fast", "core", "blazing","performance")

##Attaching words associated with Storage and Memory
storage_memory = c("memory-space", "memory", "storage","ram","space","capacity")

###Attaching words associated with Camera
camera = c("camera", "picture", "pixel", "pixels", "webcam", "front", "back", "rear", "flash", "zoom","images","photo")

###Attaching words associated with Wirelss
wireless = c("wireless", "3g", "4g", "connectivity", "broadband", "bluetooth", "network", "wifi", "sim", "dual", "dualsim")

###Attaching words associated with Price
price = c("price", "overpriced", "exhorbitant", "expensive", "cheap", "affordable", "economical", "warranty","guarantee")

###Attaching words associated with OS
os = c("os", "operating", "android", "ios", "windows","userfriendly","blackberry","windows")

###Attaching words associated with Battery
battery = c("battery", "batterylife", "recharge", "drain", "drains", "day", "ram")

###Attaching words associated with Aesthtics & Accessibility
aesthetics = c("design", "quality", "shape", "keyboard", "interface", "easy", "ease", "handle", "fits", "fit", "backlight", "durable", "rugged", "break", "breaks", "fragile", "crack", "cracks","picturequaqlity")

##Attaching words associated with Usage
usage= c("read", "reading", "book", "books", "watch", "watching", "movies", "stream", "streaming", "music", "surf", "browse","game","gaming","listening","listen","downloading","download","email")

tablet_lexicon= c(weight,display_media,processor,storage_memory,camera,wireless,price,os,battery,aesthetics,usage)

# Combining title and content together
Review <-paste(rd$Title, rd$Content, sep = " ")
Review <- tolower(Review)

#Creating a corpus of the reviews and removing stopwords and punctuation and numbers
review <- Corpus(VectorSource(Review))
temp = tm_map(review,removeWords,stopwords("english"))
temp = tm_map(review,removePunctuation)
temp = tm_map(temp,removeNumbers)

# Converting the corpus into a TDM
review <- TermDocumentMatrix(temp,control=list(minWordLength=1))

#Calculating sum to get the totalk frequency of the words
review_sum = rollup(review, 2, na.rm=TRUE, FUN = sum)
review_sum_df = as.data.frame(as.matrix(review_sum))
names(review_sum_df)= c("Frequency")
review_sum_df$words<-rownames(review_sum_df)

# Extracting the frequency for the words in the tablet lexicon created
tablet_features = review_sum_df[review_sum_df$words %in% tablet_lexicon,]
feature = c()
x = ""
for (i in 1:length(tablet_features$words)){
  if (tablet_features$words[i] %in% weight){x = "weight"}
  else if (tablet_features$words[i] %in% display_media){x ="display & media"}
  else if (tablet_features$words[i] %in% processor){x = "processor"}
  else if (tablet_features$words[i] %in% storage_memory){x = "storage & memory"}
  else if (tablet_features$words[i] %in% camera){x = "camera"}
  else if (tablet_features$words[i] %in% wireless){x ="wireless"}
  else if (tablet_features$words[i] %in% price){x = "price"}
  else if (tablet_features$words[i] %in% os){x = "os"}
  else if (tablet_features$words[i] %in% battery){x = "battery"}
  else if (tablet_features$words[i] %in% aesthetics){x = "aesthetics"}
  else if (tablet_features$words[i] %in% usage){x= "usage"}
  feature = c(feature,x)
}
tablet_features$feature = feature 

tablet_features$weight = ifelse(tablet_features$feature == "weight",tablet_features$Frequency,0)
tablet_features$display_media = ifelse(tablet_features$feature == "display & media",tablet_features$Frequency,0)
tablet_features$processor = ifelse(tablet_features$feature == "processor",tablet_features$Frequency,0)
tablet_features$storage_memory = ifelse(tablet_features$feature == "storage & memory",tablet_features$Frequency,0)
tablet_features$camera = ifelse(tablet_features$feature == "camera",tablet_features$Frequency,0)
tablet_features$wireless = ifelse(tablet_features$feature == "wireless",tablet_features$Frequency,0)
tablet_features$price = ifelse(tablet_features$feature == "price",tablet_features$Frequency,0)
tablet_features$os = ifelse(tablet_features$feature == "os",tablet_features$Frequency,0)
tablet_features$battery = ifelse(tablet_features$feature == "battery",tablet_features$Frequency,0)
tablet_features$aesthetics = ifelse(tablet_features$feature == "aesthetics",tablet_features$Frequency,0)
tablet_features$usage = ifelse(tablet_features$feature == "usage",tablet_features$Frequency,0)

```

# Ranking the features  and finding the top 20
```{r}
tablet_features_2 = tablet_features[order(tablet_features$Frequency,decreasing = TRUE),]
top_20 = tablet_features_2[1:20,c(1,2)]
```


# Plotting the top 20 features
```{r}
par(mfrow = c(1,1))
top_20$words <-factor(top_20$words, levels=top_20[order(top_20$Frequency), "words"])
top_features <- ggplot(top_20,aes(x = words , y = Frequency))
top_features <- top_features + geom_bar(stat = "identity") + coord_flip() +
  labs(title = "Top Features")
top_features
```


#Wordcloud of all the features
```{r}
par(mfrow = c(1,1))
pal2 <- brewer.pal(8,"Dark2")
wordcloud(tablet_features_2$words,tablet_features_2$Frequency, scale=c(8,.2),min.freq=3,
max.words=100, random.order=FALSE, rot.per=.15, colors=pal2)
```


#Wordcloud of individual product characteristics

The below code plots a wordcloud for each of the tablet feature, highlighting the most frequent word associated with each fetaure.
```{r}
# Change plot size to 4 x 3
options(repr.plot.width=9, repr.plot.height=9)
par(mfrow = c(4,3))

wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,4]), col = "red")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,5]), col ="blue")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,6]), col ="lightseagreen")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,7]), col= "orange")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,8]), col ="purple")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,9]), col = "hotpink")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,10]), col ="chocolate")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,11]), col ="deeppink3")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,12]), col = "darkturquoise")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,13]), col ="darkmagenta")
wordcloud(tablet_features_2[1:115,2],as.numeric(tablet_features_2[1:115,14]), col ="forestgreen")

product_categories = data.frame(Attributes = c("Weight","Display & Media","Processor","Storage & Memory", "Camera","Wireless","Price","os","Battery","Aesthetics","Usage"), Weights = c(10:20))

pal2 <- brewer.pal(8,"Dark2")
wordcloud(product_categories$Attributes,product_categories$Weights, scale=c(8,.2),min.freq=3,
max.words=Inf, random.order=FALSE, rot.per=.15, colors=pal2)
```

